Unveiling the 2022 Iran Protests: Insights from HRANA's Dataset

### 2024-04-18 paper/paper.qmd

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Entries Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

@fig-arrests-detainees illustrates the cumulative count of arrests and detainees identified over time during the protests.Detainees are people who were held in custody temporarily for less than 24 hours, while arrests consist of individuals who may still be in prison. By tracking both metrics, we can gain valuable insights into the authorities' response to the protests and the way they treat individuals involved. The area chart displays the progression of these two metrics, providing insights into the trend of arrests and detentions throughout the specified period. The light gray area represents the cumulative count of individuals arrested, while the dark gray area represents the cumulative count of detainees identified.

@@

@fig-Daily-Death shared valuable insights regarding the changing dynamics of protester fatalities over a period of 158 days. The data shows that the number of protester deaths fluctuated from day to day, indicating varying levels of intensity in the conflict or protests. Some days had a high number of deaths (such as September 30th), while there were no deaths or even a decrease in deaths on other days. This data can provide useful insights into the dynamics of the conflict, helping us to understand trends, identify critical periods of escalation, and evaluate the effectiveness of interventions aimed at reducing violence and protecting civilians.

@@

```
@fig-Percentage-Death-all-categories shows the percentage breakdown of deaths among protesters, children, and security personnel during the 158-day protest period. According to @fig-Percentage-Death-all-categories, out of the 671 deaths that occurred during a specific timeframe, the majority (approximately 79%) were protesters. Unfortunately, children also suffered significant losses, accounting for around 10.6% of the total deaths. Security personnel represented a slightly smaller proportion, comprising approximately 10.4% of the fatalities. This visualization highlights the need to protect vulnerable groups affected by the ongoing conflict, especially protesters and children.

@@

In @fig-ratio-universities-to-cities, Each point on the plot represents a specific date, and the y-axis represents the ratio of universities to cities involved. For example, if the ratio is 0.5 on a certain date, it means that there are, on average, half as many universities involved in protests as there are cities. Based on this ratio, we can observe that there were initial changes in the ratio of universities to cities involved in protests, ranging from 0 to around 0.85. However, there is an overall increasing trend in the ratio, suggesting that more universities are getting involved relative to the number of cities involved in protests. Towards the end of the data, the ratio stabilizes around 0.87 to 0.88, indicating that the rate of increase in university involvement might have slowed down, reaching a plateau. Although there are changes in the ratio over time, there is still an upward trend in the level of university involvement relative to the cities involved. This data suggests a gradual increase in university involvement in protests, which could be influenced by various factors such as changes in university policies, the progression of the protest movement, and the dynamics of activism within different regions.

@@

During a period of 158 days, a series of protests took place, which resulted in a tragic outcome. In total, 671 people lost their lives, including 530 protesters, 71 children, and 70 security personnel. This means that protesters make up a significant 79% of the casualties, while children and security personnel accounted for 10.6% and 10.4%, respectively. These numbers highlight the devastating human cost of political unrest and the need for peaceful and constructive dialogue. Moreover, The participation of 144 universities and 165 cities highlights the broad scope of the movement, which includes people from different demographics and regions in Iranian society. The ratio of universities to cities involved in the protests, which ranges from 0 to approximately 0.87, reflects the evolving nature of activism and dissent across educational and urban landscapes. The arrest of 19,763 people, among them 723 students, highlights the severe measures taken by the government and the challenges faced by protesters who are trying to express their dissent. These numbers are a stark reminder of the pressing need to address the root causes of gender inequality, political oppression, and human rights violations in Iran.

>>>>

kable(selected_columns, 
      format = "markdown", 
      align = "c",
      caption = "Ten Random Observation Compiled By HRANA",
      label = "tbl-protest-data")|>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)

@@

@fig-arrests-detainees illustrates the cumulative count of arrests and detainees identified over time during the protests. Detainees are people who were held in custody temporarily for less than 24 hours, while arrests consist of individuals who may still be in prison. By tracking both metrics, we can gain valuable insights into the authorities' response to the protests and the way they treat individuals involved. The area chart displays the progression of these two metrics, providing insights into the trend of arrests and detentions throughout the specified period. The light gray area represents the cumulative count of individuals arrested, while the dark gray area represents the cumulative count of detainees identified.

@@

@fig-Daily-Death shared valuable insights regarding the changing dynamics of protester fatalities over a period of 158 days. The data shows that the number of protester deaths fluctuated from day to day, indicating varying levels of intensity in conflict or protests. Some days had a high number of deaths (such as September 30th), while there were no deaths or even a decrease in deaths on other days. This data can provide useful insights into the dynamics of the conflict, helping us to understand trends, identify critical periods of escalation, and evaluate the effectiveness of interventions aimed at reducing violence and protecting civilians.

@@

```
@fig-Percentage-Death-all-categories shows the percentage breakdown of deaths among protesters, children, and security personnel during the 158-day protest period. According to @fig-Percentage-Death-all-categories, out of the 671 deaths that occurred during a specific time frame, the majority (approximately 79%) were protesters. Unfortunately, children also suffered significant losses, accounting for around 10.6% of the total deaths. Security personnel represented a slightly smaller proportion, comprising approximately 10.4% of the fatalities. This visualization highlights the need to protect vulnerable groups affected by the ongoing conflict, especially protesters and children.

@@

In @fig-ratio-universities-to-cities, each point on the plot represents a specific date, and the y-axis represents the ratio of universities to cities involved. For example, if the ratio is 0.5 on a certain date, it means that there are, on average, half as many universities involved in protests as there are cities. Based on this ratio, we can observe that there were initial changes in the ratio of universities to cities involved in protests, ranging from 0 to around 0.85. However, there is an overall increasing trend in the ratio, suggesting that more universities are getting involved relative to the number of cities involved in protests. Towards the end of the data, the ratio stabilizes around 0.87 to 0.88, indicating that the rate of increase in university involvement might have slowed down, reaching a plateau. Although there are changes in the ratio over time, there is still an upward trend in the level of university involvement relative to the cities involved. This data suggests a gradual increase in university involvement in protests, which could be influenced by various factors such as changes in university policies, the progression of the protest movement, and the dynamics of activism within different regions.

@@

During a period of 158 days, a series of protests took place, which resulted in a tragic outcome. In total, 671 people lost their lives, including 530 protesters, 71 children, and 70 security personnel. This means that protesters make up a significant 79% of the casualties, while children and security personnel accounted for 10.6% and 10.4%, respectively. These numbers highlight the devastating human cost of political unrest and the need for peaceful and constructive dialogue. Moreover, the participation of 144 universities and 165 cities highlights the broad scope of the movement, which includes people from different demographics and regions in Iranian society. The ratio of universities to cities involved in the protests, which ranges from 0 to approximately 0.87, reflects the evolving nature of activism and dissent across educational and urban landscapes. The arrest of 19,763 people, among them 723 students, highlights the severe measures taken by the government and the challenges faced by protesters who are trying to express their dissent. These numbers are a stark reminder of the pressing need to address the root causes of gender inequality, political oppression, and human rights violations in Iran.
